---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# foodpls

<!-- badges: start -->
<!-- badges: end -->

This is a bot that can be used to check out an Amazon cart. Use at your own risk!

## Installation

``` r
# install.packages("devtools")
devtools::install_github("aedobbyn/foodpls")
```

## Configuration

* Add some Amazon cookies to `data-raw/cookies_template.csv` and change the file name to `data-raw/cookies.csv`
  * This allows Selenium to bypass the 2FA that you'd normally have to go through when you're not already logged in
  * You can find these by opening the Chrome inspector on an Amazon page, heading to the Applications tab, then looking under Cookies
  
* Save your email in an environment variable called `EMAIL`
* Save your Amazon password in an environment variable called `AMAZON_PASS`

e.g.

```
Sys.setenv(EMAIL="ratatouille@gmail.com")
```

## Run

There are three main functions in this package. 

* `get_in`: logs you in
* `checkout`: checks out your cart and navigates you to the page where you would select a delivery time if one is available
* `buy`: selects the first available delivery time if it's available. If it's not, it keeps refreshing the page until a certain number of tries is reached or a time limit is reached, or both.

`run` evaluates all of these in order.


```{r eval=FALSE}
library(foodpls)
```

There are two carts to choose from: `"whole foods"` or `"amazon fresh"`.

```{r, eval=FALSE}
run(cart = "whole foods")
```

The `...` args to `run` are passed to `buy`.

```{r, eval=FALSE}
run(cart = "amazon fresh", n_tries = 3, sleep_time = 2)
```

